A quantitative framework for investigating the reliability of network construction

### 2018-03-07 manuscript/CI_interactions.tex
There, now just need to add posterior property results

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}). In our dataset, the entire 95\% credible interval was (0.013, 0.049). We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed cooccurring is below 0.05. To be 95\% confident that the interaction probability for these species is below 0.01 would require 139 observed co-occurrences with no interaction.

      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreasesy. The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.001 would require 15, 39, and 229 observed co-occurrances, respectively.

@@

%DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo ! 
[[Update these two figs with Zillis data.]]
      \begin{figure}[ht]
        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases. \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component. This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
        \label{Salix_pdfs}
        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
        \end{figure}

      \begin{figure}[ht]
        \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters. With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction. Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value. The large ticks along the x-axis indicate the number of samples associated with each of these points. Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network. In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrances was 0.364. All pairs of species therefore have $\lambda$\textless0.5.}
        \label{Salix_cdfs}
        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}

>>>>

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}). In our dataset, the entire 95\% credible interval was (0.013, 0.049). We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed cooccurring is below 0.05. As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.

      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreasesy. The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrances, respectively.

@@

%DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo ! 
[[Update these two figs with Zillis data.]]
      \begin{figure}[ht]
        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases. \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component. This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
        \label{Salix_pdfs}
        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
        \end{figure}

      \begin{figure}[ht]
        \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters. With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction. Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value. The large ticks along the x-axis indicate the number of samples associated with each of these points. Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network. In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrances was 0.364. All pairs of species therefore have $\lambda$\textless0.5.}
        \label{Salix_cdfs}
        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
